Dissertation draft

### 2023-07-13 Texfiles/Draft1.tex
Mainly subjective life tables

\cite{mitchell_et_al_1999} - this is empirical
\cite{friedman_warshawsky_qje_1990} - this is theory

\cite{friedman_warshawsky_chicago_1988} - this is more theory. Probably good to have read.

@@

. \textit{Continue
      chat about how elderly population is growing and private pension pots are growing in size, could be worth referencing
      latest census data so we seem super up to date, look at IFS data about the growth of DC pensions as well. }
\textbf{I will do this this afternoon}

>>>>

@@

\cite{vidalmelia_lejarragagarcia_munich_2004} have some interesting results. Need to talk about that.

\subsection{Methodology}

I first solve a modified retirement lifecycle model. Retirees face
\begin{equation*}
      E(U) = \sum_{t = x}^{110 - w}[u(c_{t})]
\end{equation*}
